Visualization of [fulle name] Fractional Integrals

### 2019-03-25 fractional/CMJ style files/article-template.tex
started fleshing out the introduction of the paper

It can be argued that fractional calculus is as old as classical calculus itself. The father of calculus, Leibnis, mentiones the notion of a fractional 
order derivative in a letter he sent to L'Hospital. In this letter he answers a question L'Hospital poses. Liouville and Riemann laid much of the groundwork which was 
needed to define the Riemann-Liouville fractional integral [Laurent’].

It was pointed out at the first international conference on fractional calculus in New Haven (USA) in 1974 that literature lacked an acceptable geometric and physical
interpretation of the fractional integral []. Consequently the last few decades has seen a number of papers that attempt to rectify this. There now exists probabilistic interpretations, 
geometric interpretations and ecenomic interpretations of the fractional integral.

In this paper we present a novel geometric interpretation of the Riemann-Liouville fractional integral. The interpretation we present here is quite useful from 
a pedigogical point of view as

>>>>

It can be argued that fractional calculus is as old as classical calculus itself. Leibniz, who is regarded by many as the farther of calculs, invented the following notation: $\frac{d^n f(x)}{d^n x}$ Leibniz mentiones the notion of a fractional 
order derivative in a letter he sent to L'Hospital. In this letter he is responding to a question L'Hospital posed. L'Hospital asked the question: ``What if $n$ be a $\frac{1}{2}$?''. Liouville and Riemann laid much of the groundwork which was 
needed to define the Riemann-Liouville fractional integral [Laurent’].

It was pointed out at the first international conference on fractional calculus in New Haven (USA) in 1974 that literature lacked an acceptable geometric and physical
interpretation of the fractional integral and that this has been the case for more than 300 years []. Consequently the last few decades has seen a number of papers that attempt to rectify this. There now exists probabilistic interpretations, 
geometric interpretations and ecenomic interpretations of the fractional integral.

In this paper we present a novel geometric interpretation of the Riemann-Liouville fractional integral. The interpretation we present here is especially useful from 
a pedigogical point of view as it is similar in nature to the definition of classical integration. In ordinary integration we can interpret the integral 
as an infinite sum of rectangular infinitesimals. In this paper, we demonstrate at the hand of examples that the Riemann-Liouville fractional integral can be interpreted 
as an infinite sum of non-rectangular infinitesimals whose shape is determined by the order of integration $\alpha$ and the integration limit $x$.
